Reliable feature point matching without the use of geometric constraints

### 2013-06-06 text/clustering.tex
Version 2.3

Figure \ref{fig:result_accumulated} shows the accumulated results on the 
\emph{Murals} dataset. It shows that \emph{MMC} and \emph{MM} is overall 
superior to both \emph{SIFT} and \emph{Isodata} which uses geometric 
constraints when tested on image pairs with no assurance of overlap 
depicting simple planar scenes. Figure \ref{fig:result_faces} 
illustrates the result on a particular image pair from the \emph{Murals} 
dataset. For an example of a real life use case \ref{fig:result_pitts} 
shows the results on potentially overlapping image pairs generated from 
a typical holiday scene with partial overlap and slight viewport 
change. As can be seen in figure \ref{fig:result_viewport}, \emph{MMC} 
consistently outperforms \emph{SIFT} across different magnitudes of the 
viewport change. For the results on image 1 and 3 from the \emph{Graf} 
dataset, see figure \ref{fig:result_graf}.
Generally all plots show good results by \emph{Isodata} when only the 
best matches are returned, but when the thresholds are more lenient the 
quality of the returned matches degrades quickly and \emph{MMC} and 
\emph{MM} yield better results.

In terms of performance, table \ref{table:running_times} shows the 
running time of the four algorithms over $100$ image pairs of $250$px by 
$250$px. These numbers should be interpreted with the knowledge that 
much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
python while \emph{MM} and \emph{SIFT} makes use of opencv to execute 
computationally intensive operations in C++ which renders it much 
faster.
%
\begin{savenotes}
\begin{table}
	\centering
	\small
\begin{tabular}{l*{4}{c}}
	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
	\\
	\noalign{\smallskip} 
	%
	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
\end{tabular}
\caption{Running times as tested on a Intel(R) Core(TM) i5-3550 CPU @ 
3.30GHz with 8Gb memory}
\label{table:running_times}
\end{table}
\end{savenotes}
%

>>>>

Figure \ref{fig:result_graf} shows the results for 100 image pairs 
generated from img1 and img3 of the \emph{Graf} image set. The plot 
illustrates how \emph{Isodata} performs well to begin with, but as we 
permit more matches \emph{MM} and \emph{MMC} show superior results. To 
generalize this result, figure \ref{fig:result_accumulated} displays the 
accumulated result over the \emph{Murals} dataset as well as the 
\emph{Graf} pair tested in fig. \ref{fig:result_graf}. In total 900 
image pairs were generated from 9 source pairs. This plot confirms the 
accuracy of \emph{MMC} and \emph{MM} over a bigger data set. As can be 
seen in figure \ref{fig:result_viewport}, the results of \emph{MMC} are 
general across different magnitudes of the viewport change.

For an example of a real life use case \ref{fig:result_pitts} shows the 
results on potentially overlapping image pairs generated from a typical 
holiday scene with partial overlap and slight viewport change.

In terms of performance, table \ref{table:running_times} shows the 
running time of the four algorithms over $100$ image pairs of $250$px by 
$250$px. These numbers should be interpreted with the knowledge that 
much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
python while \emph{MM} and \emph{SIFT} makes use of opencv to execute 
computationally intensive operations in C++ which renders it much 
faster. While \emph{SIFT}, \emph{MM} and \emph{Isodata} can be 
implemented in $O(nlogn)$ where $n$ is the total amount of feature 
points, \emph{MMC} currently has a complexity of $O(n^2)$ due to the 
construction of a similarity matrix of the feature points. It is however 
possible to approximate this in $O(nlogn)$, something that might be 
pursued in future work.
%
\begin{savenotes}
\begin{table}
	\centering
	\small
\begin{tabular}{l*{4}{c}}
	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
	\\
	\noalign{\smallskip} 
	%
	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
\end{tabular}
\caption{Running times as tested on a Intel(R) Core(TM) i5-3550 CPU @ 
3.30GHz with 8Gb memory}
\label{table:running_times}
\end{table}
\end{savenotes}
%
